### 2019-03-04 report/final-report.tex
bib stuff

The products of this investigation include several published
papers~\cite{bijective-synthesis, quotient-synthesis, symmetric-synthesis}
describing and evaluating our algorithms, as well as open-source 
code~\cite{GitHub} that implements those algorithms in (several variants of) a
prototype tool called \Optician{}.  In this report,
we summarize our key methods, results, and findings, focusing
on the core algorithms for bijective synthesis, quotient synthesis, and
simple symmetric synthesis.

@@

We have written
papers~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}
describing and evaluating our algorithms and produced open-source
code~\cite{GitHub} that implements those algorithms in (several variants of) a
tool called \Optician{}.  In this report, we summarize some of our key methods,
results and findings, focusing on the core algorithms for bijective synthesis
and quotient synthesis.

@@

We implemented our synthesis algorithms in the OCaml programming language
and integrated them into Boomerang system, where they are available as open
source code~\cite{GitHub}\bcp{Two more pointers needed}.  Users of Boomerang
can write lenses by hand, specify them as synthesis tasks, or do a
combination of both.

>>>>

The products of this investigation include several published
papers~\cite{bijective-synthesis, quotient-synthesis, symmetric-synthesis}
describing and evaluating our algorithms, as well as open-source 
code~\cite{BijectiveOptician,QuotientOptician,SymmetricOptician} that implements those algorithms in (several variants of) a
prototype tool called \Optician{}.  In this report,
we summarize our key methods, results, and findings, focusing
on the core algorithms for bijective synthesis, quotient synthesis, and
simple symmetric synthesis.

@@

We have written
papers~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}
describing and evaluating our algorithms and produced open-source
code~\cite{BijectiveOptician,QuotientOptician,SymmetricOptician} that implements those algorithms in (several variants of) a
tool called \Optician{}.  In this report, we summarize some of our key methods,
results and findings, focusing on the core algorithms for bijective synthesis
and quotient synthesis.

@@

We implemented our synthesis algorithms in the OCaml programming language
where they are available as open
source code~\cite{BijectiveOptician,QuotientOptician,SymmetricOptician}.
